Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-08 manuscript/climate_sensitivity_draft.Rmd
changed abstract
#131

### Summary
- As climate change drives increased drought in many forested regions around the world, mechanistic understanding of the factors conferring drought resistance in trees is increasingly important. The dendrochronological record provides a window through which we can understand how tree size and species’ traits shape growth responses during droughts.

@@

- Individual-level drought resistance decreased with tree height, which was strongly correlated with exposure to higher evaporative demand and solar radiation. The potentially greater rooting volume of larger trees did not confer an advantage in sites with low topographic wetness index. Resistance was greater among species whose leaves experienced less shrinkage upon desiccation and*, marginally, those whose leaves* lost turgor (wilted) at more negative water potentials.

>>>>

### Summary
- As climate change drives increased drought in many forested regions around the world, mechanistic understanding of the factors conferring drought tolerance in trees is increasingly important. The dendrochronological record provides a window through which we can understand how tree size and species’ traits shape growth responses during droughts.

@@

- Individual-level drought tolerance (resistance, recovery, and resilience) decreased with tree height, which was strongly correlated with exposure to higher evaporative demand and solar radiation. The potentially greater rooting volume of larger trees did not confer a resistance advantage in sites with low topographic wetness index, but marginally increased recovery and resilience. *Resistance and resilience were greater among species whose leaves experienced less shrinkage upon desiccation and, while recovery was greatest among those whose leaves lost turgor (wilted) at more negative water potentials.*
